Why does preregistration increase the persuasiveness of evidence? A Bayesian rationalization.

### 2023-02-16 manuscript.Rmd
Apply suggestions from code review

<!---outline-structure--->
To form such an objective for preregistration, we first introduce some tools of Bayesian philosophy of science and map the exploration/confirmation distinction onto a dimensional quantity we call "theoretical risk" [a term borrowed from @meehlTheoreticalRisksTabular1978, but formalized as the probability of proving a hypothesis wrong, if it does not hold], which is inversely related to the type-I error rate in statistical test theory.

@@

1. Researchers judge the evidence for or against a hypothesis rationally.
2. They expect other researchers to apply the same rational process.
2. All else being equal, researchers try to increase the expected epistemic value for other researchers.

@@

To summarize, we showed that both higher theoretical risk and lower uncertainty about theoretical risk lead to higher expected epistemic value across a variety of measures.
The former result, that increasing theoretical risk leads to higher expected epistemic value, reconstructs the appeal and central goal of preregistration ofr confirmatory research agendas.
However, theoretical risk is something researcher have only limited control over, for example, theories are often vague and ill-defined, resources are limited, and increasing theoretical risk usually decreases detectability of a hypothesized effect (a special instance of this trade-off is the well known tension between type-I error and statistical power).
While we believe that preregistration is always beneficial, it might be counterproductive to pursue high theoretical risk if the research context is inappropriate for strictly confirmatory research.
Specifically, appropriateness here entails the development of precise theories and the availability of necessary resources (often, large enough sample size, but also see @brandmaier2015lifespan) to adequately balance detectability against theoretical risk.

>>>>

<!---outline-structure--->
To form such an objective for preregistration, we first introduce some tools of Bayesian philosophy of science and map the exploration/confirmation distinction onto a dimensional quantity we call "theoretical risk" [a term borrowed from @meehlTheoreticalRisksTabular1978, but formalized as the probability of proving a hypothesis wrong, if it does not hold], which is inversely related to the type-I error rate in null hypothesis testing.

@@

@@

To summarize, we showed that both higher theoretical risk and lower uncertainty about theoretical risk lead to higher expected epistemic value across a variety of measures.
The former result, that increasing theoretical risk leads to higher expected epistemic value reconstructs the appeal and central goal of preregistration of confirmatory research agendas.
However, theoretical risk is something researcher have only limited control over, for example, theories are often vague and ill-defined, resources are limited, and increasing theoretical risk usually decreases detectability of a hypothesized effect (a special instance of this trade-off is the well known tension between type-I error and statistical power).
While we believe that preregistration is always beneficial, it might be counterproductive to pursue high theoretical risk if the research context is inappropriate for strictly confirmatory research.
Specifically, appropriateness here entails the development of precise theories and the availability of necessary resources (often, large enough sample size, but also see @brandmaier2015lifespan) to adequately balance detectability against theoretical risk.
